Schema Evolution in Interactive Programming Systems

### 2024-08-28 paper.tex
tweak abstract
clarify that manual evolution isn't a requirement in principle, it's just the status quo

Many improvements to programming have come from shortening feedback loops, for example with Integrated Development Environments, Unit Testing, Live Programming, and Distributed Version Control.
\emph{Schema evolution} is a roadblock to feedback in many situations that deserves greater attention.
When requirements on the shape of data change then existing data must be migrated into the new shape, and existing code must be modified to suit. In many cases these adaptations must be performed manually, or with ad hoc code. Manual schema evolution not only delays feedback but since it occurs outside the purvey of version control tools it also interrupts collaboration.

>>>>

Many improvements to programming have come from shortening feedback loops, for example with Integrated Development Environments, Unit Testing, Live Programming, and Distributed Version Control.
A barrier to feedback that deserves greater attention is \emph{Schema Evolution}.
When requirements on the shape of data change then existing data must be migrated into the new shape, and existing code must be modified to suit. Currently these adaptations are often performed manually, or with ad hoc code. Manual schema evolution not only delays feedback but since it occurs outside the purvey of version control tools it also interrupts collaboration.
